Water Quality at Toronto Beaches

### 2024-09-23 paper/paper.qmd
Creae and add to quarto weekly and monthly summary tables

---
title: "Water Quality at Toronto Beaches"
subtitle: "An analysis of e-coli rates in toronto beaches 2007-2024"
author: 
  - Jacob Gilbert
thanks: "Code and data are available at: https://github.com/JfpGilbert0/toronto-beaches-water-quality."
date: today
date-format: long
abstract: ""
format: pdf
---

@@

## Monthly data
```{python}
#| echo: false
# Execute the external Python script
#with open(f"../code/model_generation/monthly_summary.py") as script_file:
#    exec(script_file.read())
```

@@

## Weekly Data

```{python}
#| echo: false
# Execute the external Python script
with open(f"../code/model_generation/dow_bar.py") as script_file:
    exec(script_file.read())
```

>>>>

---
title: "Water Quality at Toronto Beaches"
subtitle: "An analysis of e-coli rates in toronto beaches 2007-2024"
author: 
  - Jacob Gilbert
thanks: "Code and data are available at: https://github.com/JfpGilbert0/toronto-beaches-water-quality."
date: today
date-format: long
abstract: ""
format: pdf
jupyter: python3
---

@@

## Monthly data
```{python}
#| echo: false
# Execute the external Python script
with open(f"../code/model_generation/monthly_summary.py") as script_file:
    exec(script_file.read())
summary
```

@@

## Weekly Data
```{python}
#| echo: false
# Execute the external Python script
with open(f"../code/model_generation/weekly_summary.py") as script_file:
    exec(script_file.read())
summary
```
```{python}
#| echo: false
# Execute the external Python script
with open(f"../code/model_generation/dow_bar.py") as script_file:
    exec(script_file.read())
```
